\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics

### 2023-02-08 article/main.tex
🚧 (article): Section 2 done, WIP
🚧 (article): Save point, WIP
✨ (article): Methodology done.
🚧 (article): WIP save point for revision
🚧 (article): Save point
🚧  (article): Review, Anna part 1 a

\documentclass[preprint,12pt]{elsarticle}
%% Use the option review to obtain double line spacing
% \documentclass[preprint,review,12pt]{elsarticle}

\input{journal/journal.tex}

\input{packages/packages.tex}
\input{acronyms/acronyms.tex}

@@

\input{frontmatter/frontmatter.tex}
\input{sections/01-introduction.tex}
\input{sections/02-artificial-neural-networks.tex}
\input{sections/03-heuristics.tex}
\input{sections/04-hyper-heuristics.tex}
\input{sections/05-probability.tex}
\input{sections/06-bayesian-hyper-heuristics.tex}
\input{sections/07-methodology.tex}
\input{sections/08-results.tex}
\input{sections/09-conclusion.tex}

>>>>

% \documentclass[preprint,12pt]{elsarticle}
%% Use the option review to obtain double line spacing
\documentclass[preprint,review,12pt]{elsarticle}

\usepackage{acro}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{subcaption}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}

% Adam
\DeclareAcronym{Adam}{
      short = Adam,
      long = \textit{adaptive moment estimation}
}

% ANOVA
\DeclareAcronym{ANOVA}{
      short = ANOVA,
      long = \textit{analysis of variance}
}

\DeclareAcronym{Adagrad}{
      short = Adagrad,
      long = \textit{adaptive gradients}
}

\DeclareAcronym{Adadelta}{
      short = Adadelta,
      long = \textit{adaptive learning rate}
}

\DeclareAcronym{RMSProp}{
      short = RMSProp,
      long = \textit{root mean squared error propagation}
}

\DeclareAcronym{PSO}{
      short = PSO,
      short-plural-form = PSOs,
      long = \textit{particle swarm optimisation},
      long-plural-form = \textit{particle swarm optimisers}
}

\DeclareAcronym{Momentum}{
      short = Momentum,
      long = \textit{momentum}
}

\DeclareAcronym{NAG}{
      short = NAG,
      long = \textit{Nesterov accelerated gradients}
}

\DeclareAcronym{GA}{
      short = GA,
      short-plural-form = GAs,
      long = \textit{genetic algorithm},
      long-plural-form = \textit{genetic algorithms}
}

\DeclareAcronym{GP}{
      short = GP,
      long = \textit{genetic programming},
}

% Artificial Intelligence
\DeclareAcronym{AI}{
      short = AI,
      long = \textit{artificial intelligence}
}

% Artificial Neural Network
\DeclareAcronym{ANN}{
      short = ANN,
      short-plural-form = ANNs,
      long = \textit{artificial neural network},
      long-plural-form = \textit{artificial neural networks}
}

% Artificial Neuron
\DeclareAcronym{AN}{
      short = AN,
      short-plural-form = ANs,
      long = \textit{artificial neuron},
      long-plural-form = \textit{artificial neurons}
}

% Bayesian Hyper-Heuristic
\DeclareAcronym{BHH}{
      short = BHH,
      short-plural-form = BHHs,
      long = \textit{Bayesian hyper-heuristic},
      long-plural-form = \textit{Bayesian hyper-heuristics}
}

% Binary Cross-Entropy
\DeclareAcronym{BinXE}{
      short = BinXE,
      long = \textit{binary cross entropy}
}

% Categorical Cross-Entropy
\DeclareAcronym{CatXE}{
      short = CatEX,
      long = \textit{categorical cross entropy}
}

% Feedforward Neural Network
\DeclareAcronym{FFNN}{
      short = FFNN,
      short-plural-form = FFNNs,
      long = \textit{feedforward neural network},
      long-plural-form = \textit{feedforward neural networks}
}

% Hyper-Heuristic
\DeclareAcronym{HH}{
      short = HH,
      short-plural-form = HHs,
      long = \textit{hyper-heuristic},
      long-plural-form = \textit{hyper-heuristics}
}

% Differential Evolution
\DeclareAcronym{DE}{
      short = DE,
      long = \textit{differential evolution}
}

% Gradient Descent
\DeclareAcronym{GD}{
      short = GD,
      long = \textit{gradient descent}
}

% Leaky Rectified Linear Unit
\DeclareAcronym{LReLU}{
      short = LReLU,
      long = \textit{leaky rectified linear unit}
}

% Maximum A Posteriori
\DeclareAcronym{MAP}{
      short = MAP,
      long = \textit{maximum a posteriori estimation}
}

% Maximum Likelihood Estimation
\DeclareAcronym{MLE}{
      short = MLE,
      long = \textit{maximum likelihood estimation}
}

% Machine Learning
\DeclareAcronym{ML}{
      short = ML,
      short-plural-form = MLs,
      long = \textit{machine learning},
      long-plural-form = \textit{machine learnings}
}

% Mean Absolute Error
\DeclareAcronym{MAE}{
      short = MAE,
      long = \textit{mean absolute error}
}

% Mean Squared Error
\DeclareAcronym{MSE}{
      short = MSE,
      long = \textit{mean squared error}
}

% Rectified Linear Unit
\DeclareAcronym{ReLU}{
      short = ReLU,
      long = \textit{rectified linear unit}
}

% Root Mean Squared Error
\DeclareAcronym{RMSE}{
      short = RMSE,
      long = \textit{root mean squared error}
}

% Sparse Categorical Cross-Entropy
\DeclareAcronym{SparseCatXE}{
      short = SparseCatXE,
      long = \textit{sparse categorical cross entropy}
}

% Stochastic Gradient Descent
\DeclareAcronym{SGD}{
      short = SGD,
      long = \textit{stochastic gradient descent}
}

% Hidden Markov Model
\DeclareAcronym{HMM}{
      short = HMM,
      short-plural-form = HMMs,
      long = \textit{hidden Markov model},
      long-plural-form = \textit{Hidden Markov Models}
}

% Backpropagation
\DeclareAcronym{BP}{
      short = BP,
      long = \textit{backpropagation}
}

\DeclareAcronym{MH}{
      short = MH,
      short-plural-form = MHs,
      long = \textit{meta-heuristic},
      long-plural-form = \textit{meta-heuristics}
}

% Probability Mass Function
\DeclareAcronym{PMF}{
      short = PMF,
      short-plural-form = PMFs,
      long = \textit{probability mass function},
      long-plural-form = \textit{probability mass functions}
}

\journal{Information Sciences}

@@

\begin{frontmatter}
	\title{\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics}

	\tnotetext[note1]{It is recommended that the article be viewed/printed in colour.}

	\affiliation[aff:tuks]{
		organization={University of Pretoria},
		% addressline={Lynnwood Rd},
		city={Pretoria},
		postcode={0002},
		state={Gauteng},
		country={South Africa}
	}

	\affiliation[aff:stellenbosch]{
		organization={Stellenbosch University},
		% addressline={Ryneveld Street},
		city={Stellenbosch},
		postcode={7602},
		state={Western Cape},
		country={South Africa}
	}

	\affiliation[aff:wits]{
		organization={University of the Witwatersrand},
		% addressline={1 Jan Smuts Ave},
		city={Johannesburg},
		postcode={2000},
		state={Gauteng},
		country={South Africa}
	}

	\author[aff:tuks]{\corref{cor1}A.N.~Schreuder}
	\ead{an.schreuder@up.ac.za}
	\author[aff:tuks]{A.S.~Bosman}
	\ead{annar@cs.up.ac.za}
	\author[aff:stellenbosch]{A.P.~Engelbrecht}
	\ead{engel@sun.ac.za}
	\author[aff:wits]{C.W.~Cleghorn}
	\ead{christopher.cleghorn@wits.ac.za}

	\cortext[cor1]{Corresponding author}

	\begin{abstract}
		The process of training \acfp{FFNN} can benefit from an automated process where the best heuristic to train the network is sought out automatically by means of a high-level probabilistic-based heuristic. This research introduces a novel population-based \acf{BHH} that is used to train \acfp{FFNN}. The performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours. The chosen heuristic pool consists of classic gradient-based heuristics as well as \acf{MH}. The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics. The \acs{BHH} is shown to be able to train \acp{FFNN} well and provide an automated method for finding the best heuristic to train the \acp{FFNN} at various stages of the training process.
	\end{abstract}

	\begin{highlights}
		\item A novel \acf{HH} selection operator is used that focuses on using Bayesian statistics to calculate the probability that a heuristic should be selected in order to efficiently train \acfp{FFNN}. The resulting \acs{HH} is referred to as the \acf{BHH}.

		\item The results of the empirical study show with statistical significance that the \acs{BHH} performs generally well on multiple problems. It is shown that, for each problem, the \acs{BHH} performance is comparable to the best low-level heuristics included in the heuristic selection pool.

		\item The results of the empirical study show that the \acs{BHH} is able to select the best heuristic to train \acp{FFNN} in general. This relieves researchers from the burden of having to do this selection process manually through trial and error.

		\item The results of the empirical study show that the \acs{BHH}, given a diverse set of lower-level heuristics, will generally produce good results when applied to multiple problems at the same time.

		\item Finally, the results of the empirical study show that the \acs{BHH} is capable of utilising \textit{a priori} \footnote{Latin word, meaning ``from what comes before''.} knowledge in which a predefined selection bias is used for heuristics that are known to be well suited for certain problems.
	\end{highlights}

	\begin{keyword}
		hyper-heuristics \sep meta-learning \sep feedforward neural networks \sep supervised learning \sep Bayesian statistics
	\end{keyword}
\end{frontmatter}

% INTRODUCTION
\section{Introduction}
\label{sec:introduction}

A popular field of focus for studying \acfp{ANN} is the process by which these models are trained. \acp{ANN} are trained by optimisation algorithms known as heuristics. Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train \acp{ANN} is required in order to yield optimal results. This process is often non-trivial and time-consuming. Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.

A recent suggestion related to the field of \textit{meta-learning} is to dynamically select and/or adjust the heuristic used throughout the training process. This approach focuses on the hybridisation of learning paradigms. One such form of hybridisation of learning paradigms is that of hybridisation of different \textit{heuristics} as they are applied to some optimisation problem \citep{ref:burke:2013}. These methods are referred to as \acfp{HH} and focus on finding the best heuristic in \textit{heuristic space} to solve a specific problem.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems \citep{ref:burke:2013}. However, research on the application of \acp{HH} in the context of \acs{ANN} training is scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acf{FFNN} training.

This research takes a particular interest in developing a population-based, selection \acs{HH} that makes use of probability theory and Bayesian statistical concepts to guide the heuristic selection process. This paper presents a novel \acf{BHH}, a new high-level heuristic that utilises a statistical approach, referred to as \textit{Bayesian analysis}, which combines prior information with new evidence to the parameters of a selection probability distribution. This selection probability distribution is the mechanism by which the \acs{HH} selects appropriate heuristics to train \acp{FFNN} during the training process.

The remainder of this article is structured as follows: Section \ref{sec:anns} provides background information on \acp{ANN}. Section \ref{sec:heuristics} provides details on various types of heuristics that have been used to train \acp{FFNN}. Section \ref{sec:hhs} presents background information on \acp{HH} and meta-learning. Section \ref{sec:probability} presents background information on probability theory. Section \ref{sec:bhh} presents the developed \acs{BHH}. Section \ref{sec:methodology} presents a detailed description of the empirical process and the setup of each experiment. Section \ref{sec:results} provides and discusses the results of the empirical study. Section \ref{sec:conclusion} summarises the research that is done along with a brief overview of the findings.

% ARTIFICIAL NEURAL NETWORKS
\section{Artifical Neural Networks}
\label{sec:anns}

This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}. In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.

\textit{Training} is the process whereby the weights of the \acs{FFNN} are systematically changed with the aim of improving the \textit{performance} of the \acs{FFNN}. Finding the optimal weights that produce the best performance on a given task is an optimisation problem. The optimisation algorithm used to find the optimal weights is referred to as a \textit{heuristic}. Heuristics search for possible solutions in the solution-space and make use of information from the search space to guide to process.

During the training process, the \acs{FFNN} is exposed to data while trying to produce some target outcome. The degree to which the produced outcome differs from the target outcome is referred to as \textit{loss}. Since training of \acp{FFNN} is an optimisation problem, the goal of the training process is to minimise the loss. The loss is calculated using an error function.

% HEURISTICS
\section{Heuristics}
\label{sec:heuristics}

A heuristic refers to an algorithmic search technique that serves as a guide to a search process where good solutions to an optimisation problem are being sought out. Many different techniques have been used to train \acp{FFNN} \citep{ref:kingma:2014}. At the time of writing, the majority of work that is published on the training of \acp{FFNN} involves the use of gradient-based techniques \citep{ref:nel:2021}.

Gradient-based heuristics are optimisation techniques that make use of derivatives obtained from evaluating the \acs{ANN} error function. In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output. When using \acf{GD} to train \acp{ANN}, the gradients of the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \citep{ref:engelbrecht:2007}.

There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}. This algorithm is known as \acf{BP}. \acs{BP} was popularised by \citet{ref:werbos:1994}.

The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern. In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.

Alternative variants have been proposed that lead to better control over the convergence characteristics of \acs{SGD}. This research focuses on a number of these variants that include \acf{Momentum} \citep{ref:qian:1999}, \acf{NAG} \citep{ref:sutskever:2013}, \acf{Adagrad} \citep{ref:duchi:2011}, \acs{Adadelta} \citep{ref:zeiler:2012}, \acf{RMSProp} \citep{ref:hinton:2012} and \acf{Adam} \citep{ref:kingma:2014}.

Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \citep{ref:bengio:2000}. \citet{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space. These methods are referred to as \acp{MH}.

The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}. This also means that \acp{MH} do not necessarily require the error function to be differentiable. \citet{ref:blum:2003} provides advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often. Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}. This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}. These include \acf{PSO} \citep{ref:shi:1998}, \acf{DE} \citep{ref:price:2006} and \acfp{GA} \citep{ref:fraser:1957}.

% HYPER-HEURISTICS
\section{Hyper-Heuristics}
\label{sec:hhs}

\citet{ref:burke:2010} define \acp{HH} as search methods or learning mechanism for selecting or generating heuristics to solve computational search problems. \citet{ref:burke:2003} mention that a \acs{HH} is a high-level heuristic approach that, given a particular problem instance and a number of low-level heuristics, can select and apply an appropriate low-level heuristic at each decision point. \acp{HH} implement a form of \textit{meta-learning} that is concerned with the selection of the best heuristic from a pool of heuristics to solve a given problem. It can be said that \acp{HH} are concerned with finding the best heuristic in \textit{heuristic space}, while the underlying low-level heuristics find solutions in the feasible \textit{search/solution space}.

\citet{ref:burke:2010} proposed a classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two dimensions. These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}. For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}. For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}. Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include \citep{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying a \acs{HH} to \acs{FFNN} training.

This research takes a particular interest in a population-based, selection approach for \acp{HH}, with the particular intent of training \acp{FFNN}. In the context of population-based \acp{HH}, an entity pool exists that represents a pool of candidate solutions to the given problem. Each entity in the entity pool is assigned its own low-level heuristic from the heuristic pool. The selection of the best heuristic to apply to a candidate solution is based on the performance of the heuristic relative to that particular candidate solution at a particular point in the search process. Selection methods often make use of probabilistic approaches.

% PROBABILITY
\section{Probability}
\label{sec:probability}

In general, there are two main views to probability and statistics. These include the \textit{frequentist} and the \textit{Bayesian} view of statistics. Naturally, Bayesian statistics is based on Bayes' theorem \citep{ref:bayes:1763}.

Bayesian statistics describe the probability of an event in terms of some belief, based on previous knowledge of the event and the conditions under which the event happened \citep{ref:hackenberger:2019}. Bayes' theorem expresses how a degree of belief, expressed as a probability, should rationally change to account for the availability of related evidence.

One of the many applications of Bayes' theorem is to do statistical inference. Like \acp{FFNN}, Bayesian models need to be \textit{trained}, a process known as \textit{Bayesian analysis}. Bayesian analysis is the process by which prior beliefs are updated as a result of observing new data/evidence.

Bayesian analysis utilises the concept of conjugate priors. \citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values. The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.

% BAYESIAN HYPER-HEURISTICS
\section{Bayesian Hyper-Heuristics}
\label{sec:bhh}

This section presents the novel \acs{BHH}. The general concept of the \acs{BHH} can be summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.

Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}. Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}. Discussions follow on the most important components of the \acs{BHH}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=1.0\textwidth]{bhh_architecture.pdf}
	\caption[An illustration of
		the architecture and high level components of the \acf{BHH}.]{An illustration of
		the architecture and high level components of the \acf{BHH}.}
	\label{fig:bhh_architecture}
\end{figure}

\begin{algorithm}[htbp]
	\footnotesize
	\caption{The pseudo-code for the implementation of the \acf{BHH}}
	\label{algo:bhh}
	\begin{algorithmic}
		\State step $\gets 0$

		\State select initial heuristics
		\State initialise population and entities
		\State evaluate entities' initial position
		\State update population state

		\While{stopping condition not met}
		\For{all entities in entity pool}
		\If{selected heuristic is gradient-based}
		\State get gradients
		\EndIf

		\State apply low-level heuristic and proxy operations
		\State update population state
		\State log performance metrics to performance log

		\If {step < burn-in window size}
		\State select heuristic
		\Else
		\If {step $\mathbin{\%}$ reanalysis interval = 0}
		\State apply Bayesian analysis
		\EndIf

		\If {step $\mathbin{\%}$ reselection interval = 0}
		\State select heuristic
		\EndIf

		\If {step > replay window size}
		\State prune performance log
		\EndIf
		\EndIf
		\EndFor
		\State step $\gets$ step + $1$
		\EndWhile
	\end{algorithmic}
\end{algorithm}

\subsection{Heuristic Pool}\label{sec:bhh:heuristic_pool}

Generally speaking, the heuristic pool is a collection of low-level heuristics under consideration by the \acs{BHH}. The heuristic pool contains the set of low-level heuristics that, together with their performance information, make up the \text{heuristic space}. Importantly, the heuristic pool must consist of a diverse set of low-level heuristics with varying capabilities. This research takes an interest in including both gradient-based heuristics as well as \acp{MH} in the heuristic pool. This approach is referred to as a \textit{multi-method} approach.

\subsection{Proxies}\label{sec:bhh:heuristic:proxies}

Heuristics often maintain a set of parameters that are used to control the behaviour of the heuristic. These parameters are refered to as heuristic \textit{state}. The concept of proxies arises from the sparsity of state as maintained by different heuristics. Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics. A solution to state indifference is to \textit{proxy} heuristic state update operations. State is then maintained in two parts: primary and proxied state. Primary state refers to the state that is originally maintained by a heuristic. Proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic. The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.

\begin{table}[htbp]
	\centering
	\caption{An example of a mapping of proxied state update operation maintained by the \acs{BHH}.}
	\label{tab:bhh:heuristic_pool:proxy_mapping_example}%
	\par\bigskip
	\resizebox{0.38\textwidth}{!}{
		\begin{tabular}{ccccc}
			                                                &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
			\cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
			\cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
			                                                & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
			                                                & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
		\end{tabular}%
	}
\end{table}%

From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2. Heuristic B will outsource from \index{heuristic}heuristic A for state parameter 3. Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B for state parameters 2 and 3 respectively. In this way, all \index{heuristic}heuristics maintain all the state parameters.

\subsection{Entity Pool}\label{sec:bhh:entity_pool}

The entity pool refers to a collection or \textit{population} of \textit{entities} that each represent a candidate solution to the underlying \acs{FFNN} being trained. The \acs{BHH} selects from the heuristic pool a low-level heuristic to be applied to an individual entity. The outcome of this selection process is a mapping table that tracks which heuristic has been selected for which entity. These heuristic-entity combinations are applied to the underlying \acs{FFNN}. The \acs{BHH} tracks the performance of each of these combinations throughout the training process in a performance log.

Entities represent candidate solutions to the model's trainable parameters (weights) and other heuristic-specific state parameters. These state parameters are referred to as \textit{local} state. Entities are treated as physical \textit{particles} in a hyper-dimensional search environment. Entities model concepts from physics. For example, the candidate solution is represented as the entity's position. The velocity and acceleration is then analogous to the gradient and momentum of the entity respectfully \cite{ref:eberhart:1995}. Examples of entity state parameters, as derived from various low-level heuristics, include entity position, velocity, gradient, position delta, first and second moments of the gradient, the loss, personal best positions, losses, and so on. The entity state parameters are updated by the associated heuristic.

The population state refers to a collection of parameters that are shared between the entities in the population. Population state is also referred to as \textit{global} state and represents the population's memory. The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not individual heuristic. Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.

\subsection{Performance Log}\label{sec:bhh:performance_log}

Heuristic selection probability is calculated based on heuristic-entity performance over time. Evidence of heuristic-entity performance is thus required for the \acs{BHH} to learn. Historical heuristic-entity performance outcomes are stored in a performance log. The performance log tracks information such as the current step, selected heuristic, associated entity, the loss achieved and so on. Since the performance log can become very big, only a sliding window of the performance history is maintained at each step in the learning process. The sliding window is also referred to as a \textit{replay} window/buffer.

\subsection{Credit Assignment Strategy}
\label{sec:bhh:credit_assignment_strategy}

The credit assignment strategy is a mechanism that assigns a discrete credit indicator to heuristics that perform well, based on their performance metrics such as loss. The credit assignment strategy implements a component of the ``move acceptance'' process as proposed by \citet{ref:ozcan:2006} and addresses the credit assignment problem as discussed by \citet{ref:burke:2010}. A good credit assignment strategy will correctly allocate credit to the appropriate heuristic-entity combination. This research implements the following credit assignment strategies to choose from: \textit{ibest} (iteration best), \textit{pbest} (personal best), \textit{gbest} (global best), \textit{rbest} (replay window best), and \textit{symmetric}, where credit is assigned to all entity-heuristic combinations, regardless of their performance.

\subsection{Selection Mechanism}\label{sec:bhh:selection_mechanism}

The \acs{BHH} implements a probabilistic predictive model based on the fundamentals of the Na\"{\i}ve Bayes algorithm. The \acs{BHH} thus distinguishes between the following events: \textbf{$\boldsymbol{H}$}, the event of observing \textit{heuristics}, \textbf{$\boldsymbol{E}$}, the event of observing \textit{entities}, and \textbf{$\boldsymbol{C}$}, the event of observing \textit{credit assignments} that indicate that the credit assignment \textit{performance criteria} are met. By Bayes' theorem, the selection mechanism implemented by the \acs{BHH} is given as

\begin{equation}
	\label{eq:bhh:selection_mechanism:predictive_model_prop_to}
	\begin{split}
		P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi}) &\propto P(\boldsymbol{E} \vert \boldsymbol{H}; \boldsymbol{\phi}) P(\boldsymbol{C} \vert \boldsymbol{H}; \boldsymbol{\psi}) P(\boldsymbol{H} \vert \boldsymbol{\theta})
	\end{split}
\end{equation}

The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \sim Beta(\gamma_{1}, \gamma_{0})$. In the aforementioned, $K$ is the heuristic pool size and $J$ is the entity pool size. The parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ are referred to as concentration parameters. The concentration parameters parameterises the prior probability distributions. \ref{app:naive_bayes} provides mathematical derivations of the predictive model.

\subsection{Optimisation Step}\label{sec:bhh:optimisation_step}

The intent of the \acs{BHH} is to gather evidence that can be used to update prior beliefs about which heuristics perform well during training. These beliefs are represented by the concentration parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$. A change in prior beliefs is represented by a change in these concentration parameters. Specifically, it can be said that the optimisation process implemented by the \acs{BHH} updates \textit{pseudo counts} of events that are observed in the performance logs. These pseudo counts track the occurrence of a heuristic, an entity, and resulting performance of these two elements. Through the credit assignment strategy, these pseudo counts are biased towards entity-heuristic combinations that meet performance requirements and yield credit allocations.

Generally, there are two different techniques that are used to train Naïve Bayes classifiers. The frequentist approach implements \acf{MLE} and the Bayesian approach implements \acf{MAP}.

\subsubsection{Maximum A Posteriori Estimation}\label{sec:bhh:optimisation_step:map}

Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters. This process is referred to as \textit{Bayesian analysis}. Bayesian analysis makes use of the \textit{posterior} probability distribution. The concentration update operations yielded by \acs{MAP} are given as follows:

\begin{equation}
	\label{eq:bhh:optimisation_step:map:alpha_update_operation}
	\begin{split}
		\alpha_{k}(t+1) = N_{k} + \alpha_{k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:beta_update_operation}
	\begin{split}
		\beta_{j,k}(t+1) = N_{j,k} + \beta_{j,k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma1_update_operation}
	\begin{split}
		\gamma_{1,k}(t+1) = N_{1,k} + \gamma_{1,k}(t)
	\end{split}
\end{equation}

\begin{equation}
	\label{eq:bhh:optimisation_step:map:gamma2_update_operation}
	\begin{split}
		\gamma_{2,k}(t+1) = N_{0,k} + \gamma_{2,k}(t)
	\end{split}
\end{equation}

\noindent
where $N_{k}$ is a summary variable denoting the count of occurrences of heuristic $k$, $N_{j}$ is a summary variable denoting the count of occurrences of entity $j$, $N_{j,k}$ is a summary variable denoting the count of occurrences of heuristic $k$ for entity $j$, $N_{1,k}$ and $N_{0,k}$ are summary variables denoting the count of occurrences where heuristic $k$ meets performance requirements and where heuristic $k$ does not not meet performance requirements.

It can be said that the \acs{BHH} implements a Gaussian process \citep{ref:gortler:2019}. Since the reselection of heuristics happens at regular intervals, the outcome of a selection in one iteration may influence the outcome of another in the next iteration, making the implementation of the \acs{BHH} a \acf{HMM} \citep{ref:rabiner:1986}.

\subsection{Hyper-Parameters}\label{sec:bhh:hyper_parameters}

The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.

% METHODOLOGY
\section{Methodology}
\label{sec:methodology}

This section provides the details of the implementation of the empirical process. At a high level the experimental procedure consist of a comparison between the \acs{BHH} and standalone low-level heuristics. A number of datasets, models and heuristics are specified. Throughout the empirical process, the use of a \acs{BHH} baseline configuration is used.

\subsection{BHH Baseline}\label{sec:methodology:baseline_bhh}

The \acs{BHH} baseline is a name given to a specific configuration of the \acs{BHH} which has been found to provide a reasonable baseline performance. The baseline configuration is used as the cornerstone configuration from which all other heuristics and their configurations are evaluated. The \acs{BHH} baseline configuration is given in Table \ref{tab:methodology:bhh_baseline_configuration}. In Table \ref{tab:methodology:bhh_baseline_configuration}, the heuristic pool configuration, \textit{all}, refers to a configuration where the heuristic pool contains all the low-level heuristics, including all gradient-based heuristics and \acp{MH}.
